---
title: "a very nice test?"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
layout: post
title: "a very nice test"
author: roel_hogervorst
modified:
categories: blog
excerpt: 
tags: [beginner, git, version control, sourcetree, mvp]
image:
  feature:
date: 2016-12-10
share: true
---



# A big ass title

Now some text 
Far one far wherever winked much showy thrust far a one more cockatoo hamster spent then a sighed as moral and in and.

Beside and regarding skeptic and this crud dear aimlessly insect strange far goose hideously salmon staidly camel endearing mongoose crud habitually stout a.

Parrot strewed palpable sat hilarious and rabbit much and followed after weasel frowned flirtatiously dear frustrating echidna greyhound more well so thus har


```{r first_chunk}
#install.packages("dplyr")
#library(dplyr)
plot(iris$Sepal.Length, iris$Sepal.Width, col = iris$Species)
    
```

And some text to finish it off.

More barring wow and some alas darn the antelope kangaroo one belched perceptible opposite placed dishonest manta irresistibly yet that one barring less opened
random text from [this website](http://www.randomtext.me/)
